---
title: param_analysis_name analysis report
date: today
bibliography: _template/references.bib
csl: _template/vancouver_superscript.csl
knitr:
  opts_chunk:
    echo: false
    message: false
    warning: false
format:
    html:
        grid:
            body-width: 1200px
            margin-width: 20px
        theme: _template/litera_edited.scss
        embed-resources: true
        fig-width: 10
        fig-height: 5
        fig-dpi: 200
        toc: true
        toc-location: left
        toc-depth: 4
        toc-expand: 2
        include-in-header:
            - text: <link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Atkinson+Hyperlegible:ital,wght@0,700;1,700&family=Poppins:ital,wght@0,400;0,600;1,400;1,600&display=swap" rel="stylesheet">
params:
  analysis_name: param_analysis_name
  panning_id: param_panning_id
---

## Introduction

This is the WNP report for `r params$analysis_name`. The report is interactive: click around on the plots and use the download buttons to export the tables/sequences for further analysis!

Want to know more about how the results were generated? Check the bottom of the report 👇

```{r}
# we have to source the pre render script every time which is annoying
source("_template/pre_render_script.R")
source("_template/panning_pre_render.R")
```

## Top 100 most abundant sequences in each round

The trees in this section visualise the 100 most abundant **clones** in each round. Abundance is measured in counts per million (CPM) and so can be compared between rounds.

```{r}
#| echo: false
#| message: false
#| warning: false

render_child <- function(file, i) {
  res = knitr::knit_child(
   text = xfun::read_utf8("./_template/_abundance_tree.qmd"),
   envir = rlang::env(this_round = i - 1, name = paste0("Round ", i - 1)),
   quiet = TRUE
  )
  cat(res, sep = '\n')
  cat("\n")
}
```

```{r}
#| results: "asis"
#| echo: false
purrr::iwalk(sort(unique(metadata$round)), render_child)
```

## Enriched clusters

### PCA plot & top 100s

```{r}
# get enriched sequences
# get enriched sequences
enriched_clustered <- determine_enriched(
    all_counts_filtered, as.numeric(params$panning_id), logfc_cutoff = 1.5)

# create the pca plot & find top 100
cluster_pca_plot_data <- make_cluster_pca_data(enriched_clustered, as.numeric(params$panning_id), metadata, max_round = max(metadata$round))
plot_cluster_pca(cluster_pca_plot_data$pca_data, cluster_pca_plot_data$table_data, params$analysis_name)

# write to file so they can be downloaded
diversity_100 <- cluster_pca_plot_data$table_data %>%
    filter(cluster_lead %in% cluster_pca_plot_data$top_100_diversity) %>%
    select(cluster_lead, trimmed_nt_sequence)
top_100_diversity_nt_seq <- Biostrings::DNAStringSet(diversity_100$trimmed_nt_sequence)
names(top_100_diversity_nt_seq) <- diversity_100$cluster_lead

Biostrings::writeXStringSet(
    top_100_diversity_nt_seq,
    file = paste0(
        str_replace_all(params$analysis_name, " ", "_"),
        "_top_100_diversity_nt_seq.fasta"))

enrichment_100 <- cluster_pca_plot_data$table_data %>%
    filter(cluster_lead %in% cluster_pca_plot_data$top_100_enrichment) %>%
    select(cluster_lead, trimmed_nt_sequence)
top_100_enrichment_nt_seq <- Biostrings::DNAStringSet(enrichment_100$trimmed_nt_sequence)
names(top_100_enrichment_nt_seq) <- enrichment_100$cluster_lead

Biostrings::writeXStringSet(
    top_100_enrichment_nt_seq,
    file = paste0(
        str_replace_all(params$analysis_name, " ", "_"),
        "_top_100_enrichment_nt_seq.fasta"))
```

{{< downloadthis r paste0(str_replace_all(params$analysis_name, " ", "_"), "_top_100_enrichment_nt_seq.fasta") dname=r paste0(str_replace_all(params$analysis_name, " ", "_"), "_top_100_enrichment_nt_seq") label="Download top 100 (by enrichment) FASTA" icon=file-earmark-arrow-down type=secondary class=data-button id=top100_enrichment >}}

{{< downloadthis r paste0(str_replace_all(params$analysis_name, " ", "_"), "_top_100_diversity_nt_seq.fasta") dname=r paste0(str_replace_all(params$analysis_name, " ", "_"), "_top_100_diversity_nt_seq") label="Download top 100 (by diversity) FASTA" icon=file-earmark-arrow-down type=secondary class=data-button id=top100_diversity >}}

### Tree of the top 100 most enriched clusters

```{r}
#| echo: false
#| message: false
#| warning: false

# use suppressMessages to stop the stupid using gonnet message
enriched_tree_data <- suppressMessages(make_interactive_tree_data(
    enriched_clustered, which_round = max(metadata$round),
    id = as.numeric(params$panning_id), enriched = TRUE))

enriched_tree <- plot_interactive_tree(
    enriched_tree_data$tree_data,
    enriched_tree_data$table_data,
    name = params$analysis_name,
    enriched = TRUE)

```

```{r}
#| fig-width: 10
#| fig-height: 1
enriched_tree$legend
```

```{r}
enriched_tree$interactive_plot
```

## Analysis method

TODO: put a mermaid diagram of the method here

lkjsadlkasjdlkjwqijjwnkjnmznc,jnasjknd